\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-12 syntax.tex
Mention how partial recursor is provable in plugin and thus trivially modelled by Metatheory

>>>>

% With sealing on hand, our metatheory is directly corresponding to our Coq's implementation.

Partial recursor and computational axiom is modelled like any other recursors and theorems.\footnote{This is partially because the partial recursor is provable in our Plugin.} Recall that the sealed context is corresponding to a module type. Partial recursor is constructed directly using \ruleref{Rec-Constr} like any other recursors in our metatheory. With trivial sealing, and with concrete inductive type and partial recursor exposed in the context, we will have judgemental equality for beta-equality of the partial recursor, to prove the computational axiom. The only difference is that, partial recursor doesn't support user extension in plugin implementation but our encoding supports that.
